---
title: "PlotDrafts"
author: "Stephen Pelkofer"
date: "3/18/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Imports
Packages needed

```{r}
library(tidyverse)
library(highcharter) #interactive plotting library
library(tibbletime)
library(ggforce)
library(scales)
library(ggtext)
library(reactable)
```

## Data

```{r}
GameLogs <- read.csv("C:/MAMP/htdocs/FinalGameLogs.csv")
levels(GameLogs$Distance) <- c("0-4ft","10-14ft","15-19ft","20-24ft","25-29ft","5-9ft")
GameLogs$Game_Date <- as.Date(GameLogs$Game_Date)
```


```{r}
BoxScores <- read.csv("../data/BoxScores.csv")
PlayerInfo <- BoxScores %>%
  distinct(idPlayer,Player,urlPlayerHeadshot)
Subset <- PlayerInfo %>%
  filter(Player == "Anthony Davis")
```

```{r}
PlayerClusters <- read.csv("../data/PlayerClusters.csv")
```


## Plotting

# Custom Color Paletes
```{r}
BlueSeqColors <- c( #light to dark blue
   "#f1eef6",
   "#bdc9e1",
   "#74a9cf",
   "#2b8cbe",
   "#045a8d"
)

QualColors <- c( #category/qualitative/groups
  '#386cb0',
  "#7fc97f",
  "#beaed4",
  "#fdc086",
  "#ffff99"
)
ScatterOppacity <- c(
  "rgba(55,126,184,.70)",
  "rgba(255,127,0,.85)"
)
```


# (1.a) Shots Defended vs DFG% Scatter
Resource: http://rstudio-pubs-static.s3.amazonaws.com/470388_85579e7a31b8402ebbc26ba86e6100ca.html
Filters: Shots Defended, Distance, Team, Opponent, Season
Ideas:
- Change between shots/36 and total shots


```{r}
DFG_Percentage <- GameLogs %>%
  filter(Season == "2019-20",
         Distance == "0-4ft") %>%
  group_by(idPlayer,Player,Distance) %>%
  summarise(T_DFGM = sum(DFGM), T_DFGA = sum(DFGA), Min = sum(minutes)) %>%
  mutate(DFG_Percent = round(T_DFGM/T_DFGA,3), ShotsDefended_Per36 = round((T_DFGM/Min)*36,1)) %>%
  filter(T_DFGA >= 150)

hchart(DFG_Percentage, "scatter",opacity = 0.65,
       hcaes(x = "ShotsDefended_Per36", y = "DFG_Percent",opacity = .5,
                                        group = "Distance",
                                        name = "Player", DFGA_36  = "ShotsDefended_Per36", 
                                        DFGEfficiency = "DFG_Percent", Distance = "Distance")) %>%
  hc_tooltip(pointFormat = "<b>{point.name}</b><br />DFGA/36: {point.DFGA_36}<br />DFG%: {point.DFGEfficiency}") %>%
  hc_title(text = "DFGA vs. DFG%") %>%
  hc_subtitle(text = "NBA 2019-2020 Season") %>%
  hc_credits(enabled = TRUE,
             text = "data via stats.nba.com",
             style = list(
               fontSize = "10px"
               )
             ) %>%
  hc_add_theme(hc_theme_elementary()) %>%
  hc_colors(ScatterOppacity)
```

# (1.b) DFG% Line by Team

```{r}
Running_DFGP <- GameLogs %>%
  filter(Season == "2019-20",
         Distance == "10-14ft",
         Team == "MIL") %>%
  group_by(Team,Game_Date) %>%
  summarise(DFGM = sum(DFGM), DFGA = sum(DFGA))
```


```{r}
rolling <- rollify(mean,window = 5,na_value = 0)
Running_DFGP <- GameLogs %>%
  filter(Season == "2019-20",
         Distance == "10-14ft",
         Team == "MIL") %>%
  group_by(Team,Game_Date) %>%
  summarise(DFGM = sum(DFGM), DFGA = sum(DFGA)) %>%
  mutate(DFGP = round(DFGM/DFGA,2),
         RollingDFGP = round(if_else(rolling(DFGP) == 0, lag(DFGP), rolling(DFGP)),2))

hchart(Running_DFGP, "spline", hcaes(x = "Game_Date", y = "RollingDFGP", group = "Team",
                                        team = "Team", Date  = "Game_Date",
                                        DFGP = "RollingDFGP")) %>%
  hc_tooltip(pointFormat = "<b>{point.team}</b><br />DFG%: {point.DFGP}") %>%
  hc_title(text = "DFG% Season Trend") %>%
  hc_credits(enabled = TRUE,
             text = "data via stats.nba.com",
             style = list(
               fontSize = "10px"
               )
             ) %>%
  hc_add_theme(hc_theme_elementary()) %>%
  hc_colors(QualColors[2])

```





# (2) DFG% Rating Table
Resource: https://glin.github.io/reactable/articles/womens-world-cup/womens-world-cup.html
Ideas:
- vs league average
- percentile (nba already does this)


# (3) Shot zone map
Resource
https://github.com/toddwschneider/ballr/blob/master/court_themes.R

Ideas:
- Custom area or polygon chart? Only need tooltip to show DFG%
- How to draw court lines over it?

```{r}
PercentileRanks <- GameLogs %>%
  filter(Season == "2019-20") %>%
  group_by(idPlayer,Player,Distance) %>%
  summarise(DFGM = sum(DFGM),DFGA = sum(DFGA)) %>%
  pivot_wider(id_cols = c(idPlayer, Player), 
              names_from = Distance, 
              values_from = c(DFGM,DFGA),
              values_fill = list(DFGM = 0, DFGA = 0)) %>%
  transmute("0-9ft" = sum(`DFGM_0-4ft`,`DFGM_5-9ft`)/sum(`DFGA_0-4ft`,`DFGA_5-9ft`),
         "10-19ft" = sum(`DFGM_10-14ft`,`DFGM_15-19ft`)/sum(`DFGA_10-14ft`,`DFGA_15-19ft`),
         "20-24ft" = sum(`DFGM_20-24ft`)/sum(`DFGA_20-24ft`),
         "25-29ft" = sum(`DFGM_25-29ft`)/sum(`DFGA_25-29ft`)
         ) %>%
  replace_na(list("0-9ft" = 0, "10-19ft" = 0, "20-24ft" = 0, "25-29ft" = 0))

PercentileRanks$zero_nine_zone <- round(percent_rank(desc(PercentileRanks$`0-9ft`)),2)
PercentileRanks$ten_nineteen_zone <- round(percent_rank(desc(PercentileRanks$`10-19ft`)),2)
PercentileRanks$twenty_twentyfour_zone <- round(percent_rank(desc(PercentileRanks$`20-24ft`)),2)
PercentileRanks$twentyfour_twentynine_zone <- round(percent_rank(desc(PercentileRanks$`25-29ft`)),2)

```


```{r}
zones <- read.csv("ShotZones.csv")
PlayerSelection <- PercentileRanks %>%
  filter(idPlayer == 2544)

player_ranks <- tibble(
  zone = c("zero_nine_zone","ten_nineteen_zone","twenty_twentyfour_zone","twentyfour_twentynine_zone"),
    Percentile = c(PlayerSelection$zero_nine_zone[1],
    PlayerSelection$ten_nineteen_zone[1],
    PlayerSelection$twenty_twentyfour_zone[1],
    PlayerSelection$twentyfour_twentynine_zone[1])
  ) %>%
  mutate(color = case_when(
    Percentile < .1667 ~ ShotZoneColors[6],
    Percentile < .3333 ~ ShotZoneColors[5],
    Percentile < .50 ~ ShotZoneColors[4],
    Percentile < .6666 ~ ShotZoneColors[3],
    Percentile < .8333 ~ ShotZoneColors[2],
    Percentile >= .8333 ~ ShotZoneColors[1],
    )) %>%
  arrange(zone)

player_map_color <- c(player_ranks$color)
zones <- zones %>% left_join(player_ranks, by = c("desc"="zone"))
```


```{r}
ShotZoneLables <- tibble(
  x = c(0,0,0,0),
  y = c(10,19,27,32),
  label = c(PlayerSelection$zero_nine_zone[1],
    PlayerSelection$ten_nineteen_zone[1],
    PlayerSelection$twenty_twentyfour_zone[1],
    PlayerSelection$twentyfour_twentynine_zone[1]
  )
)
```




```{r}
library(plotly)
source("C:/Users/Spelk/Desktop/Georgia Tech Analytics/CSE 6242/CSE6242-S20-PRJ-NBA-frontend/NBADefensiveAnalytics/R/court.R")

plot_court() +
    coord_fixed(ylim = c(0, 35), xlim = c(-25, 25)) +
    geom_polygon(
      data = zones,aes(x = x, y = y, group = desc, fill = Percentile), color = "white", alpha =.80,
      show.legend = TRUE
    )+
  scale_fill_gradient(low = "red", high = "yellow",limits = c(0,1),
                      breaks = c(.25,.50,.75),
                      labels = c("25","50","75")) +
  geom_label(data=ShotZoneLables, aes(x = x,y = y, label = scales::percent(label, accuracy = 1L)),
              color="#4d4d4d", 
              size= 5 , angle=0, fontface="bold" ) +
  ggtitle("<b style='color:#252525'>Defensive Percentile by Zone</b>")+
  theme(plot.title = element_markdown(hjust = .5),
        legend.title = element_blank(),
        legend.key.width = unit(1,"cm"),
        legend.position=c(1.05, 0.5))
  
```


# Reactable Table(s)

```{r}
CompPlayers <- tibble(
  idPlayer = c(203507,201572,	201143,	203954,1628389),
  Rk = c(1,2,3,4,5),
  Player = c("Giannis Antetokounmpo","Brook Lopez","Al Horford","Joel Embiid","Bam Adebayo"),
  SimilarityScore = c(89,75,66,52,48)
)

        
player_tbl <- reactable(
  CompPlayers,
  bordered = FALSE, 
  pagination = FALSE,
  highlight = TRUE,
  fullWidth = FALSE,
  columns = list(
    idPlayer = colDef(
      minWidth = 50,
      cell = function(value, index) {
        div(
          img(
              src = sprintf(paste("https://ak-static.cms.nba.com/wp-content/uploads/headshots/nba/latest/260x190/", 
                                  paste(value,".png", sep = ""), sep = "")),
              height = '25px',
              width = '40px',
              style = "float:left"
              )
        )
      },
      maxWidth = 50
    ),
    Rk = colDef(name = "Rk", maxWidth = 30, style = list(color = "black"),
                headerStyle = list(color = "black")),
    Player = colDef(name = "Player",minWidth = 190,style = list(color = "black"),
                    headerStyle = list(color = "black")),
    SimilarityScore = colDef(name = "Score (0-100)",minWidth = 120,style = list(color = "black"),
                             headerStyle = list(color = "black"))
  )
)

player_tbl
```


```{r}
PlayerProfile <- tibble(
  Type = c("Name","Age","Height","Weight","Team","All-Defensive Team Selections"),
  Info = c("Anthony Davis","27","6'10","253 lb", "LAL","3")
)

        
Profile <- reactable(
  PlayerProfile,
  bordered = FALSE, 
  pagination = FALSE,
  highlight = TRUE,
  fullWidth = FALSE,
  columns = list(
    Type = colDef(name = "Player Info", minWidth = 150, style = list(color = "black"),
                headerStyle = list(color = "black")),
    Info = colDef(name = "Values",minWidth = 110,style = list(color = "black"),
                    headerStyle = list(color = "black"))
)
)

Profile
```


# Player Cluster Plot
Resource:
Ideas:

```{r}
#library(plotly)
#library(gghighlight)
#library(glue)
#library(hrbrthemes)
ClusterData <- PlayerClusters %>%
  select(PLAYER_ID, x, y) %>%
  left_join(PlayerInfo, by = c("PLAYER_ID" = "idPlayer"))

ClusterScatter <- ggplot(data = ClusterData,aes(x = x, y = y)) +
  geom_point(color = "#011627", alpha = .75) +
  #gghighlight()
  labs(title = "Defensive Player Clusters",
       subtitle = glue("NBA 2019-20 Season"),
       x = "LDA 1",
       y = "LDA 2",
       caption = "See Methodology tab for details") +
  theme_minimal()
ggplotly(ClusterScatter)
```































